---
title: "simpleRegress"
author: "Evelyn Chairez"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
  
## Model WEIGHT ~ AGE  this is an example  

```{r}
simp <- lm(WEIGHT~AGE,data=bears)
plot(WEIGHT~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ HEADLEN  this is an example  

```{r}
simp <- lm(WEIGHT~HEADLEN,data=bears)
plot(WEIGHT~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ HEADWTH  this is an example  

```{r}
simp <- lm(WEIGHT~HEADWTH,data=bears)
plot(WEIGHT~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ LENGTH  this is an example  

```{r}
simp <- lm(WEIGHT~LENGTH,data=bears)
plot(WEIGHT~LENGTH,data=bears)
abline(simp)
summary.lm(simp)
```




## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 
  
Summary of all the plots  

Neck: The RSE for this graph was 43.91 while the Adjusted R-squared was 0.7476

Length: The RSE for this graph was 61.83 while the Adjusted R-squared was 0.7423

Headlen: The RSE for this graph was 67.81 while the Adjusted R-squared was  0.69 

Headwth: The RSE for this graph was 76.41 while the Adjusted R-squared was 0.6064

Age: The RSE for this graph was 81.47 while the Adjusted R-squared was 0.5073 





